% ---------------------------------------------------

\section{Teams}
\label{app:teams}

We divided our group into several sub-teams in order to better divide work. In addition to this, we also contracted additional people for specific tasks.

% ---------------------------------------------------

\subsection{Additional Contributors}

Adam Welsh is a Computer Engineering student at the University of Utah that assisted the LoRa team in development.

Derek Tinoco is a Computer Scientist that assisted in the early sensor integration process.

Aliou Tippett is a student at the University of Utah that assisted the LoRa team in development.

% ---------------------------------------------------

\subsection{Sub-Teams}

LoRa Team: Harrison LeTourneau, Jared Pratt, Adam Welsh, Aliou Tippett. This team was responsible for the design, implementation, and testing of the LoRa communication system between the vessel and the ground station.

Sensor Team: Corbin Barney, Charbel Salloum, Connor Stevens, Derek Tinoco. This team was responsible for selecting, integrating, and testing the various sensors (GPS, IMU, wind vane) used for navigation and state awareness.

ALAN Team: Corbin Barney, Charbel Salloum, Connor Stevens, Harrison LeTourneau, Jared Pratt. This team was responsible for the overall integration of the vessel, including mechanical assembly, firmware development, and on-water testing.

Embedded Team: Corbin Barney, Charbel Salloum, Connor Stevens, Harrison LeTourneau, Jared Pratt, Derek Tinoco, Adam Welsh, Aliou Tippett. This team was responsible for the preliminary test benches used to test the various components of the vessel, including the LoRa communication system and the sensor suite.

% ---------------------------------------------------